---
title: "regression_plots_salesperworker"
output: html_document
date: "2024-02-01"
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
setwd("C:/Users/young/OneDrive/Escritorio/wb-climate-pilots-bangladesh")
source("scripts/2022/regressions_salesperworker_22.R")

library(tidyr)
library(patchwork)
library(ggplot2)
library(cowplot)
```

Regression details for reference:

-   Standardized vars: "firm_age", "num_employees", "pcnt_owned_by_largest_owner", "manager_experience_yrs"

-   Equation (or replace temp with climate var): lm(sales_per_worker ~ temp + temp:firm_age + temp:size + temp:pcnt_owned_by_largest_owner + temp:manager_experience_yrs +                 temp:top_manager_female + temp:majority_national_sales + temp:obstacle_electricity +                 temp:obstacle_transport + temp:obstacle_businesslicensing +                  temp:obstacle_accesstofinance + temp:obstacle_laborregulations +                   temp:checking_savings_account + firm_age + size + pcnt_owned_by_largest_owner +                    manager_experience_yrs + top_manager_female + majority_national_sales + obstacle_electricity + obstacle_transport + obstacle_businesslicensing + obstacle_accesstofinance + obstacle_laborregulations + checking_savings_account,
                 data = reg_master,
                 weights = wstrict)


## Size

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  size <- interactions_df[2:3,] %>%   
  separate(var, into = c("vars", "category"), sep = "(?<=\\w)_(?=[A-Z])|(?<=[a-z])(?=[A-Z])")

  plot <- ggplot(size, aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ vars) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5, size = 12),
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Create axis plot
y_lab <- 
  ggplot() + 
  annotate(geom = "text", x = 1, y = 1, label = "Category", angle = 90) +
  coord_cartesian(clip = "off")+
  theme_void()

# Show in grid using patchwork
y_lab + wrap_plots(plot_list, nrow = 2) + plot_layout(widths = c(0.05,1)) + plot_annotation(
  caption = "Reference category: Large",
  theme = theme(plot.caption = element_text(size = 11)))
```


## Age & Pcnt owned by largest owner

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  age_owner <- interactions_df %>% 
    filter(var %in% c("firm_age", "pcnt_owned_by_largest_owner")) %>% 
    mutate(category = "")

  plot <- ggplot(age_owner, aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ var) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Show in grid using patchwork
wrap_plots(plot_list, nrow = 2)
```


## Manager experience & Top manager female

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  
  management <- interactions_df[5:6,] %>%
  mutate(category = "")

  plot <- ggplot(management, aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ var) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5, size = 12),
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Show in grid using patchwork
wrap_plots(plot_list, nrow = 2)
```


## Majority sales national

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  
  majority_national_sales <- interactions_df[7,] %>%
  mutate(category = "")
  
  plot <- ggplot(majority_national_sales, aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ var) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5, size = 12),
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Show in grid using patchwork
wrap_plots(plot_list, nrow = 2)
```


## Electricity - how much of an obstacle?

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  
  obstacle <- interactions_df[8:26,] %>% 
    separate(var, into = c("vars", "category"), sep = "(?<=\\w)_(?=[A-Z])|(?<=[a-z])(?=[A-Z])") %>% 
    mutate(category = gsub("Very", "VerySevere", category)) %>% 
    mutate(vars = sub("obstacle_", "", vars)) %>% 
    mutate(category = factor(category, levels = c("Minor", "Moderate", "Major", "VerySevere")))

  plot <- ggplot(obstacle[1:4,], aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ vars) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Create axis plot
y_lab <- 
  ggplot() + 
  annotate(geom = "text", x = 1, y = 1, label = "Category", angle = 90) +
  coord_cartesian(clip = "off")+
  theme_void()

# Show in grid using patchwork
y_lab + wrap_plots(plot_list, nrow = 2) + plot_layout(widths = c(0.05, 1)) + plot_annotation(
  caption = "Reference category: No",
  theme = theme(plot.caption = element_text(size = 11)))
```

## Transport - how much of an obstacle?

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  
  obstacle <- interactions_df[8:26,] %>% 
    separate(var, into = c("vars", "category"), sep = "(?<=\\w)_(?=[A-Z])|(?<=[a-z])(?=[A-Z])") %>% 
    mutate(category = gsub("Very", "VerySevere", category)) %>% 
    mutate(vars = sub("obstacle_", "", vars)) %>% 
    mutate(category = factor(category, levels = c("Minor", "Moderate", "Major", "VerySevere")))

  plot <- ggplot(obstacle[5:8,], aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ vars) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Create axis plot
y_lab <- 
  ggplot() + 
  annotate(geom = "text", x = 1, y = 1, label = "Category", angle = 90) +
  coord_cartesian(clip = "off")+
  theme_void()

# Show in grid using patchwork
y_lab + wrap_plots(plot_list, nrow = 2) + plot_layout(widths = c(0.05, 1)) + plot_annotation(
  caption = "Reference category: No",
  theme = theme(plot.caption = element_text(size = 11)))
```


## Business licensing - how much of an obstacle?

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  
  obstacle <- interactions_df[8:26,] %>% 
    separate(var, into = c("vars", "category"), sep = "(?<=\\w)_(?=[A-Z])|(?<=[a-z])(?=[A-Z])") %>% 
    mutate(category = gsub("Very", "VerySevere", category)) %>% 
    mutate(vars = sub("obstacle_", "", vars)) %>% 
    mutate(category = factor(category, levels = c("Minor", "Moderate", "Major", "VerySevere")))

  plot <- ggplot(obstacle[9:12,], aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ vars) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Create axis plot
y_lab <- 
  ggplot() + 
  annotate(geom = "text", x = 1, y = 1, label = "Category", angle = 90) +
  coord_cartesian(clip = "off")+
  theme_void()

# Show in grid using patchwork
y_lab + wrap_plots(plot_list, nrow = 2) + plot_layout(widths = c(0.05, 1)) + plot_annotation(
  caption = "Reference category: No",
  theme = theme(plot.caption = element_text(size = 11)))
```


## Access to finance - how much of an obstacle?

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  
  obstacle <- interactions_df[8:26,] %>% 
    separate(var, into = c("vars", "category"), sep = "(?<=\\w)_(?=[A-Z])|(?<=[a-z])(?=[A-Z])") %>% 
    mutate(category = gsub("Very", "VerySevere", category)) %>% 
    mutate(vars = sub("obstacle_", "", vars)) %>% 
    mutate(category = factor(category, levels = c("Minor", "Moderate", "Major", "VerySevere")))

  plot <- ggplot(obstacle[13:16,], aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ vars) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Create axis plot
y_lab <- 
  ggplot() + 
  annotate(geom = "text", x = 1, y = 1, label = "Category", angle = 90) +
  coord_cartesian(clip = "off")+
  theme_void()

# Show in grid using patchwork
y_lab + wrap_plots(plot_list, nrow = 2) + plot_layout(widths = c(0.05, 1)) + plot_annotation(
  caption = "Reference category: No",
  theme = theme(plot.caption = element_text(size = 11)))
```


## Labor regulations - how much of an obstacle?

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  
  obstacle <- interactions_df[8:26,] %>% 
    separate(var, into = c("vars", "category"), sep = "(?<=\\w)_(?=[A-Z])|(?<=[a-z])(?=[A-Z])") %>% 
    mutate(category = gsub("Very", "VerySevere", category)) %>% 
    mutate(vars = sub("obstacle_", "", vars)) %>% 
    mutate(category = factor(category, levels = c("Minor", "Moderate", "Major", "VerySevere")))

  plot <- ggplot(obstacle[17,], aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ vars) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Create axis plot
y_lab <- 
  ggplot() + 
  annotate(geom = "text", x = 1, y = 1, label = "Category", angle = 90) +
  coord_cartesian(clip = "off")+
  theme_void()

# Show in grid using patchwork
y_lab + wrap_plots(plot_list, nrow = 2) + plot_layout(widths = c(0.05, 1)) + plot_annotation(
  caption = "Reference category: No",
  theme = theme(plot.caption = element_text(size = 11)))
```


## Firm has checking/savings account 

```{r, echo=FALSE, warning=FALSE}
# Define general function
firm_var_plot  <- function(interactions_df, title_text){
  
  tax <- interactions_df[27,] %>%
  mutate(category = "")

  plot <- ggplot(tax, aes(category, coef)) + 
    geom_hline(yintercept=0, lty=2, lwd=1, colour="grey50") +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper, colour=category), 
                  lwd=1, width=0) +
    geom_point(size=3, aes(colour=category)) +
    facet_grid(. ~ var) +
    coord_flip() +
    guides(colour=FALSE) +
    labs(title = title_text, x = "", y = "") +
    theme_grey(base_size=15) +
    theme(plot.title = element_text(hjust = 0.5, size = 12),
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10))
  
  return(plot)
}

# Create plots for each climate var using function
temp_plot <- firm_var_plot(temp_interactions, "Temperature")
tempvolatility_plot <- firm_var_plot(tempvolatility_interactions, "Temperature volatility")
hotdays_plot <- firm_var_plot(hotdays_interactions, "Hot days")
spei_plot <- firm_var_plot(spei_interactions, "SPEI")

plot_list <- list(temp_plot, tempvolatility_plot, hotdays_plot, spei_plot)

# Show in grid using patchwork
wrap_plots(plot_list, nrow = 2)
```
